---
title: "Lab 00 - Hello IDS!"
author: "Abdulrahman Hesham Al Bin Ali"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Herman", "Abdulrahman", "Rudy", 
           "Matt", "Hamish"),
  github_username = c("hermansokr", "7aman4013", "RudyAdair", 
                      "matthurrerr", "hamlot12"), 
  colour = c("green", "blue", "purple", 
             "blue", "red"),
  hobby = c("drawing", "math/coding", "Cricket", 
            "badminton", "golf"),
  favourite_number = c(sample(10,size=1), 2, 5, 9, 6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Github username vs favorite number 

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favorite Number",
          title = "Correlation between username coolness and favorite number coolness")
```

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Display data as a table rather than as a graph, as this data doesn't need to be visualized. Most of the time, there will only be 1 person with each hobby, and as such this visualization is mostly useless.
